I'm a bit at a crossroads with transaction call data (txcd) and init code i.e. the data provided in a transaction. In some sense txcd and init code should live in the same public data module:

\begin{enumerate}
\item both need to be billed (4 gas per 0x00, 16 gas for nonzero bytes)
\item both need to be laid out byte by byte:
\begin{enumerate}
	\item for txcd:
	\begin{enumerate}
		\item for byte billing
		\item to build data limbs for ram instructions touching txcd
	\end{enumerate}
	\item for init code:
	\begin{enumerate}
		\item for byte billing
		\item to build limbs for the CODECOPY instruction
	\end{enumerate}
\end{enumerate}
\item both are indexed by txNum
\end{enumerate}

On the other hand we do much more with init code than with txcd. With init code we further need to

\begin{enumerate}
	\item perform jump destination analysis and replace PUSH-shadowed bytes by INVALID instructions
	\item build push values
\end{enumerate}

Something I just realized is that outside observers know the sender address and the sender nonce, it is part of the transaction data ($T_\text{n}$). Of course a connection to a permanent state must prove its validity but it's there. So we can know deployment address (which are then verified in the proof.) We can do a 2 sided plookup inclusion proof of the init code commitment into ROM. We could have both live in the same place or in different commitments

There is a further difference: the nonce update of an deployment transaction is definitive. There are no rollbacks that can take it back. So the deployment number stuff should be $=0$ or $=1$.

We can do all of this stuff in a single module. There is no issue wrt to loading code: there can only be two code fragments for such an address: init code and deployed code, there are no revert + \inst{CREATE} in this context.

The thing is that in order to connect the txcd/initcode module to ROM I require the address. And this is something we know how to produce --- the nonce is part of the block data.

Ok in essence:
\begin{enumerate}
	\item txcd is tied to a txNum
	\item init code is tied to
	\begin{enumerate}
		\item the from address
		\item its nonce delta
		\item (implicitly to a txNum)
	\end{enumerate}
	\item ROM is indexed by address, deployment number and the \col{isInitCode} bit
	\item we can
	\begin{enumerate}
		\item do the byte billing in the call data module
		\item import the stream of
		\[
			\col{isInitCode}
			\cdot
			(\addr, \col{isInitCode}, \col{byteCounter}, \col{bytes}, \col{txcdSize})
		\]
		into the ROM where they would be sent to the tuple
		\[
			(\addr, \col{isInitCode}, \col{bytecounter}, \col{rawBytes}, \codeSize)
		\]
	\end{enumerate}
\end{enumerate}