\begin{enumerate}
    \item Output columns:
        \begin{enumerate}
            \item $\limb$:
                output of the module, contains 16 bytes data.
            \item $\limbsize$:
                number of meaningful bytes of the $\limb$. Those bytes are shifted to the left with $\llarge - \limbsize$ zeros on the right;
            \item \col{LIMB\_CONSTRUCTED}:
                binary column; equals $1$ when the $\limb$ is in one of the two RLP bytestring $\widetilde{L}_{\mathrm{T}}$ or $\widetilde{L}_{\mathrm{X}}$, otherwise equals $0$;
                abbreviated to $\lc$;
            \item $\lt$:
                binary column; equals $1$ when the constructed $\limb$ is in $\widetilde{L}_{\mathrm{T}}$, otherwise equals $0$;
            \item $\lx$:
                binary column; equals $1$ when the constructed $\limb$ is in $\widetilde{L}_{\mathrm{X}}$, otherwise equals $0$;
            \item $\indext$:
                index of the current limb within the current string of $\widetilde{L}_{\mathrm{T}}$. Starts at 0 when starting a new transaction and increments by 1 when $\lc$ and $\lt$ are one; 
            \item $\indexx$:
                index of the current limb within the current string of $\widetilde{L}_{\mathrm{X}}$. Starts at 0 when starting a new transaction and increments by 1 when $\lc$ and $\lx$ are one;
            \item \toHashByProver{}:
                binary column; equals $\lc \cdot \lx$; is a selector to extract data for the prover. 
        \end{enumerate} 
    \item Columns used exclusively for lookup connexion with other modules:
        \begin{enumerate}
            \item $\absTxNum$:
		transaction number column, starts at 0 and is incremented by one when starting a new transaction.
            \item $\outgoingDataSymb\high$ and $\outgoingDataSymb\low$:
		used for lookup with the transaction data module.
            \item \CFI{}: 
                an unique (block)-identifier of a code fragment;
            \item \txRequiresEvmExecution{}:
                binary column; is 1 when the transaction requires evm execution (ie when calling a smart contract, or when a contract creation with a non-empty init code)
            \item \Phase{}:
        column used as an identifier for the lookups;
        \end{enumerate}
    \item Columns used for heartbeat
        \begin{enumerate}
            \item $\phaseRlpPrefix{}, \dots, \phaseS{}$:
                exclusive binary columns which light up in the corresponding phase.
            \item $\phasend$:
                binary column; equals $1$ on the last row of any phase, $0$ elsewhere;
            \item \txType{}:
                defines the type of transaction, can be $0$, $1$ or $2$. The phase heartbeat depends of the \transactionType{} of the transaction.
            \item \CT{}, abbreviated $\ct$:
                internal counter, byte column. Counts from 0 to $\nbstep - 1$ and resets.
            \item $\done$:
                binary column; equal to $1$ on the final row of every \ct{} cycle; equal to $0$ otherwise;
        \end{enumerate}
    \item Columns used in several phase for computation
        \begin{enumerate}
            \item $\nbstep$:
                byte column, with value between 1 and $\llarge$.
            \item $\Input k$, $k=1,2$:
                0-16 bytes data.
            \item $\byteCol{k}$, $k=1,2$:
                byte columns used for byte decompositions, and its accumulators $\acc{k}$.
            \item $\accsize$:
                byte column used to count the bytesize of one of the two $\acc{k}$.
            \item \genBit{}:
                bit columns and its accumulator \genBitAcc{}, used for bit decomposition.
            \item \Power{} abbreviate with $P$, to calculate the offset (left shifting) for the $\limb$.
            \item $\rlptsize$:
                number of bytes of $L_{\mathrm{T}}$ of the current transaction, used in \phaseRlpPrefix{} to verify the RLP prefix. Decreases by $\limbsize$ when $\lc$ and $\lt$ are one, must be 0 at the end of the transaction.
            \item $\rlpxsize$:
                number of bytes of $L_{\mathrm{X}}$ of the current transaction, used in \phaseRlpPrefix{} to verify the RLP prefix. Decreases by $\limbsize$ when $\lc$ and $\lx$ are one, must be 0 at the end of the transaction.
        \end{enumerate}
    \item Columns used only at certain phases, are null outside those phases.
        \begin{enumerate}
            \item Used when \phaseRlpPrefix{}, \phaseData{} or \phaseBeta{} are $\equiv 1$:
                \begin{enumerate}
                    \item \ispadding:
                        bit column, used to declare when there is no limb constructed in the $\ct$-loop.
                \end{enumerate}
            \item Used when \phaseData{} or \phaseAccessList{} are $\equiv 1$:
                \begin{enumerate}
                    \item \isprefix:
                        bit column, to declare when to compute a RLP prefix.
                    \item $\phasesize$:
                        similar to $\rlptsize$. Size (in bytes) of the bytestring of this phase. Usefull to compute the RLP prefix of the byte string of this phase.
                \end{enumerate}
            \item Used in \phaseData{}
                \begin{enumerate}
                    \item \indexData{}:
                        similar to \index. Index of the given limb in the data phase (phase 9). Starts at 0 at the begining of the data phase and increments by 1 after $\lc = 1$.
                    \item \dataGasCost{}:
                        gas cost of the Data. Decreases during \phase9, must be 0 at the end of the \phase9.
                \end{enumerate}
            \item Used in \phaseAccessList{} 
                \begin{enumerate}
                    \item $\Depth1$ and $\Depth2$:
                        binary columns to define loop intrication.
                    \item $\col{Addr}\high$ and $\col{Addr}\low$ used to store high and low part of the address of an \textbf{accessList} item during the \textbf{accessList} phase.
                    \item \col{ACCESS\_TUPLE\_BYTESIZE}:
                        similar to $\rlptsize$. Size (in bytes) of an \textbf{accessList} tuple.
                    \item $\nbAddr$:
                        number of Address in the \textbf{accessList}. Decreases during \phase{10}, must be 0 at the end of the \phase{10}.
                    \item $\nStorageKeysInAccessList$:
                        total number of StorageKey in the \textbf{accessList}. Decreases during \phase{10}, must be 0 at the end of the \phase{10}.
                    \item $\nStorageKeysInAccessEntry$:
                        number of StorageKey in an \textbf{accessList} tuple.
                \end{enumerate}
        \end{enumerate}
\end{enumerate}
