We impose the following general constraints on gas columns:
\begin{enumerate}
	\item the following columns are hub-stamp-constant, see section~(\ref{hub: heartbeat: constancy conditions}),
		\begin{multicols}{2}
			\begin{enumerate}
				\item \gasExpected{} \quad (\sanityCheck)
				\item \gasNext{}     \quad (\sanityCheck)
				\item \gasActual{}   \quad (\sanityCheck)
				\item \gasCost{}     \quad (\sanityCheck)
			\end{enumerate}
		\end{multicols}
	\item \If $\txExec _{i} = 0$ \Then
		\[
			\left\{ \begin{array}{lclr}
				\gasExpected _{i} & = & 0 & (\trash) \\
				\gasNext     _{i} & = & 0 & (\trash) \\
				\gasActual   _{i} & = & 0 & (\trash) \\
				\gasCost     _{i} & = & 0 & (\trash) \\
			\end{array} \right.
		\]
\end{enumerate}
The automatic vanishing constraints aren't necessary \emph{per se}.
The following constraints enforce some of the relationships between gas columns.
\begin{enumerate}[resume]
	\item \If $\peekStack _{i} = 1$ \Then
		\begin{enumerate}
			\item \If $\xAhoy_{i} = 1$ \Then $\gasNext_{i} = 0$\footnote{One may drop the ``\If $\peekStack _{i} = 1$ \Then'' precondition in the implementation.}
			\item \If $\xAhoy_{i} = 0$ \Then
				\begin{enumerate}
					\item \If $\stackDecCreateFlag _{i} + \stackDecCallFlag _{i} = 0$ \Then
						\[ \gasNext_{i} = \gasActual_{i} - \gasCost_{i} \]
					\item \If $\stackDecCreateFlag _{i} = 1$ \Then $\gasNext_{i} = \dots$ see section~(\ref{hub: instruction handling: create})
					\item \If $\stackDecCallFlag   _{i} = 1$ \Then $\gasNext_{i} = \dots$ see section~(\ref{hub: instruction handling: call})
				\end{enumerate}
		\end{enumerate}
\end{enumerate}
\saNote{}
Earlier versions of the present arithmetization featured a constraint of the form
``\If $\locNonOogExceptions _{i} = 1$ \Then $\gasCost _{i} = 0$''
where $\locNonOogExceptions _{i} \def \xAhoy _{i} - \stackOogx_{i}$.
This constraint was supposed to facilitate the job of the \gasMod{} module.
This precaution isn't required anymore as the \gasMod{} now only compares the gas cost to the available gas in case of an \oogxSH{} or in case the opcode is (predicted to be) unexceptional.

The gas cost of an instruction matters to the present arithmetization \emph{if and only if} it is either unexceptional or raises an \oogxSH{} in the arithmetization.
For exceptional instructions the \zkEvm{} sets the next gas value to $0$.
For (most) unexceptional instructions the next value of gas is (unsurprisingly) obtained by substracting the gas cost from the currently avaialble gas.
However, pricing is special for \inst{CALL}-type and \inst{CREATE}-type instructions and we defer to the relevant instruction handling section.
\begin{enumerate}[resume]
	\item \If 
		\[
			\left\{ \begin{array}{lcl}
				\hubStamp _{i + 1} & \neq & \hubStamp_{i} \\
				\txExec   _{i    } & =    & 1             \\
				\txExec   _{i + 1} & =    & 1             \\
			\end{array} \right.
		\]
		\Then we impose
		\begin{enumerate}
			\item\label{hub: generalities: gas: could blow up} \If $\cn\new_{i} = \cn_{i}$ \Then $\gasActual_{i + 1} = \gasExpected_{i + 1}$
			\item\label{hub: generalities: gas: resuming execution gas constraint} \If $\cn\new_{i} = \caller_{i}$ \Then
				$\gasActual_{i + 1} = \gasExpected_{i + 1} + \gasNext_{i}$
			\item\label{hub: generalities: gas: spawning new context} \If $\cn\new_{i} = 1 + \hubStamp_{i}$ \Then 
				\[
					\left\{ \begin{array}{lcl}
						\gasExpected_{i + 1} & = & \relevantValue            \\
						\gasActual_{i + 1}   & = & \gasExpected_{i + 1} \\
					\end{array} \right.
				\]
		\end{enumerate}
\end{enumerate}
Some details:
(\ref{hub: generalities: gas: resuming execution gas constraint}) asserts that when an execution context reaches its conclusion (as witnessed by $\cn\new_{i} = \caller_{i}$) the $\gasNext$ column on that row must contain the left over gas in the present context.
We are unable to settle the ``call gas'' or ``create gas'' provided to a child context spawned through a \inst{CREATE}-type or \inst{CALL}-type instruction at this level of generatlity, whence the \relevantValue{} in constraint~(\ref{hub: generalities: gas: spawning new context}). It is a complex question and will be settled when we deal with the processing of those instruction families.

\issue{Constraint~(\ref{hub: generalities: gas: could blow up}) could blow up if we don't handle precompiles, pure transfers and deployments with empty code correctly.}
