The \textbf{transaction data} module \txnDataMod{} is overall a simple module which serves several important and essentially independent functions.
For one it is the \textbf{main entry point for transaction data} contained in the \rlpTxnMod{} module into the ``execution environment" which is the \hubMod{} module.
Direct, un-intermediated, communication between these modules is awkward (if not impossible.)
Indeed the \rlpTxnMod{} module provides transaction data \emph{in column form} while the \hubMod{} module accepts transaction data \emph{in row form}.
The present module thus performs a simple data reformatting step ``\textbf{horizontalization}'', see section~(\ref{txn_data: constraints: horizontalization rlpTxn}).

The \txnDataMod{} also performs simple computations which occur before transaction execution proper.
These include computing the upfront gas cost of transaction, ensuring that the gas limit covers that cost and ensuring that the underlying account has sufficient balance to cover both for gas and value transfer.
It also computes the effective gas price (for \textbf{type 2} transactions) and the effective ``fee rate'' (i.e. the rate at which the \inst{COINBASE} address collects fees.)

It is also responsible for constructing the $\ABSTXNUM$ which other modules, in particular the \hubMod{}, rely on (typically under the moniker \absTxNum{}.)
This number serves as a unique identifier for the transactions found within a conflated batch.

The present module also collects select execution data, in particular as seen at the end of transaction processing.
This includes e.g. (and using notations from the \cite{EYP}):
\begin{enumerate}
        \item leftover gas $g'$,
        \item total gas refunds $A_\text{r}'$
        \item refundable gas \( \displaystyle g^* \equiv g' + \min\Big\{\Big\lfloor\frac{T_\text{g} - g'}\maxRefundQuotient\Big\rfloor, A_\text{r}'\Big\} \)
        \item status code $\Upsilon^z(\bm{\sigma}, T)$,
        \item cumulative gas consumption of the block of transactions up to this point $\Upsilon^u(\bm{\sigma}, T)$,
\end{enumerate}
The present module also serves the \txRequiresEvmExecution{} and \txCopyTxcd{} bits to the \hubMod{} module. 
The former is established in cooperation between the two modules while the second is deduced from the first in the present module.

\saNote{} Refunds are those of the \textsc{London} release of the \evm{}.
