\begin{enumerate}
    \item $\userTransactionNumber$:
	transaction number column, starts at 0 and is incremented by one when starting a new transaction. \specTodo{} renamed \texttt{USER\_TX\_NUM}
    \item $\isTxn$:
	bit column that defines the transaction perspective;
	\item $\isCmp$:
	bit column that defines the computation perspective;
	\item \col{LIMB\_CONSTRUCTED}:
    binary column;
    is equal to $1$ when the $\limb$ is part of either \rlp{} bytestrings $\locLtTilde$ or $\locLxTilde$, otherwise is equal to $0$;
    abbreviated to $\lc$;
    \item $\indext$:
    index of the current limb within the current string of $\locLtTilde$. Starts at 0 when starting a new transaction and increments by 1 when $\lc$ and $\lt$ are one; 
    \item $\indexx$:                                                       
    index of the current limb within the current string of $\locLxTilde$. Starts at 0 when starting a new transaction and increments by 1 when $\lc$ and $\lx$ are one;
    \item $\rlptsize$:
    number of bytes of $L_{\mathrm{T}}$ of the current transaction, used in \phaseRlpPrefix{} to verify the RLP prefix. Decreases by $\limbsize$ when $\lc$ and $\lt$ are one, must be 0 at the end of the transaction.
    \item $\rlpxsize$:
    number of bytes of $L_{\mathrm{X}}$ of the current transaction, used in \phaseRlpPrefix{} to verify the RLP prefix. Decreases by $\limbsize$ when $\lc$ and $\lx$ are one, must be 0 at the end of the transaction.
    \item \toHashByProver{}:
    binary column; equals $\lc \cdot \lx$; is a selector to extract data for the prover.
\end{enumerate}
Columns used for heartbeat:
\begin{enumerate}[resume]
    \item \typeZeroTx{}, \typeOneTx{}, \typeTwoTx{}:
    exclusive bit columns definibg the type of transaction. The phase heartbeat depends of the \transactionType{} of the transaction.
    \item \phaseRlpPrefix{}, \phaseChainId{}, \phaseNonce{}, \phaseGasPrice{}, \phaseMaxPriorityFeePerGas{}, \phaseMaxFeePerGas{}, \phaseGasLimit{}, \phaseTo{}, \phaseValue{}, \phaseData{}, \phaseAccessList{}, \phaseBeta{}, \phaseY{}, \phaseR{}, \phaseS{}:
    \item $\phasend$:
    binary column; equals $1$ on the last row of any phase, $0$ elsewhere;
    \item \ct{}:
	counter column; 
	either hovers around $0$ or counts continuously up from $0$ to \maxCt{} whereupon it resets;
    \item \maxCt:
	counter-constant column;
	indicates the value at which \ct{} must reset;
	\item $\done$:
    binary column; equal to $1$ on the final row of every \ct{} cycle; equal to $0$ otherwise;
\end{enumerate}
