This document was written over the span of (almost) four and a half years and has seen various contributions from former and current colleagues not all listed as authors.
We wish to acknowledge the contributions of
Alexandre \textsc{Belling},
Nicolas \textsc{Liochon} and
Théodore \textsc{Chapuis-Chkaiban},
to the overall design of the arithmetization,
Franklin \textsc{Delehelle} for developping \href{https://github.com/Consensys/corset}{\texttt{corset}},
the first iteration of our domain specific language (DSL) for constraints,
Blazej \textsc{Kolad} and
\'{E}mile \textsc{Hautefeuille} for their work on the implementation and specification.
Inputs from \linea{}'s prover team, in particular from
Alexandre \textsc{Belling},
Azam \textsc{Soleimanian} and
Bogdan \textsc{Ursu},
have shaped various portions of the specification,
in particular as it pertains to setting up interfaces with prover modules and specialized circuits for precompiles.
Furthermore, the work of the \href{https://github.com/Consensys/gnark}{\texttt{gnark}} team
in writing precompile and compression circuits has been indispensable to the realization of this spec.
Last, but certainly not least, the work of David \textsc{Pearce}
on our tooling (\href{https://github.com/Consensys/go-corset}{\texttt{go-corset}} and \texttt{zkASM})
has had a profound impact on the concrete implementation of the arithmetization,
as it pertains to writing constraints and constructing execution traces.
Several modules presented in this document have been re-written in \texttt{zkASM} and are currently running in production.

The spec presented in this document is the foundation for \linea{}'s \zkEvm{}.
It was implemented in \href{https://github.com/Consensys/linea-monorepo}{\linea{}'s monorepo},
specifically in the \href{https://github.com/Consensys/linea-monorepo/tree/main/tracer-constraints}{\texttt{constraints}}
and the \href{https://github.com/Consensys/linea-monorepo/tree/main/tracer}{\texttt{tracer}} subfolders.
Its implementation was only made possible through by working closely with the team behind
Consensys's Ethereum client \href{https://github.com/besu-eth/besu}{\texttt{Besu}}.
We wish to thank them for their excellent support and collaborative spirit.
