\def\locTransactionPhaseSum                                             {\col{tx\_phase\_sum}}
\def\locAcceptableTransactionPhaseFlagsAtFirstRowOfNewTransaction       {\txSkip_{i} + \txWarm_{i} + \txInit_{i} = 1}
In this section we constrain the binary flags $\txSkip$, $\txWarm$, $\txInit$, $\txExec$, $\txFinl$ which indicate the transaction processing phase. We enforce a phase-rotation i.e. when which bits $\txWarm$, $\txInit$, $\txExec$, $\txFinl$ get turned on and off in non-padding rows.
These phases are expected to transition as shown in figure~\ref{fig: processing phase transition graph}.

\input{figures/processing_phase_transition_graph}

\noindent We now list the corresponding constraints:
\begin{enumerate}
	\item $\txSkip$, $\txWarm$, $\txInit$, $\txExec$ and $\txFinl$ are binary;
\end{enumerate}
We define the following shorthand:
\[
	\locTransactionPhaseSum_{i}
	\define
	\left[ \begin{array}{cl}
		+ & \txSkip_{i} \\ 
		+ & \txWarm_{i} \\
		+ & \txInit_{i} \\
		+ & \txExec_{i} \\
		+ & \txFinl_{i} \\
	\end{array} \right]
\]
\begin{enumerate}[resume] \label{hub:heartbeat: tx phase sum constraints}
	\item \If $\absTxNum_{i} = 0$ \Then $\locTransactionPhaseSum_{i} = 0$;
	\item \label{hub: heartbeat: tx phase flag exclusivity}
		\If $\absTxNum_{i} \neq 0$ \Then $\locTransactionPhaseSum_{i} = 1$;
	\item \label{hub: heartbeat: acceptable tx phases at first row of new transaction}
		\If $\absTxNum_{i} \neq \absTxNum_{i - 1}$ \Then $\locAcceptableTransactionPhaseFlagsAtFirstRowOfNewTransaction$;
\end{enumerate}
The above says that on padding rows all processing flags are off while on non-padding rows \emph{precisely} one of the processing flags flags is set. Furthermore when a new transaction starts processing it either
requires no \textsc{evm}-execution ($\txSkip_{i} = 1$)
or does and starts in either the pre-warming phase ($\txWarm_{i} = 1$)
or the initialization phase ($\txInit_{i} = 1$.)
Phases follow a cyclical pattern where the order is set (the prewarming phase being optional.)
\begin{enumerate}[resume]
	\item\label{hub: heartbeat: abs tx num increments}
		\If $\absTxNum_{i} \neq 0$ \Then
		\[ \absTxNum_{i + 1} = \absTxNum_{i} + (\txFinl_{i} + \txSkip_{i}) \cdot \peekTransaction_{i} \]
\end{enumerate}
\saNote{} The expression $(\txFinl + \txSkip) \cdot \peekTransaction$ which we use above is \textbf{binary}.

The above specifies precisely, for non padding rows $i$, when $\absTxNum$ is required to change from row $i$ to row $i + 1$. It remains unchanged in all cases \emph{except} if the transaction requires no \textsc{evm}-execution and the present row peeks into transaction data \emph{or} the transaction requires \textsc{evm}-execution, is in the finalization phase and and the present row peeks into transaction data. In this case the next row thus marks the beginning of the processing of a new transaction.

We now deal with the cyclical nature of the process.

\paragraph{Transactions whose processing requires no \textsc{evm} execution}
\begin{enumerate}[resume]
	\item
		\label{hub: heartbeat: skipping phase finishes on a transaction row}
		\If \Big($\txSkip_{i} = 1$ \et $\peekTransaction_{i} = 0$\Big) \Then $\txSkip_{i + 1} = 1$;
\end{enumerate}
\saNote{} The case $\txSkip_{i} = 1$ \et $\peekTransaction_{i} = 1$ is already known: the $\absTxNum$ changes at the following row and so by the above $\locAcceptableTransactionPhaseFlagsAtFirstRowOfNewTransaction$.

\paragraph{Transactions whose processing \emph{does} require \textsc{evm} execution}
\begin{enumerate}[resume]
	\item \If $\txWarm_{i} = 1$ \Then $\txWarm_{i + 1} + \txInit_{i + 1} = 1$
	\item
		\label{hub: heartbeat: initialization phase finishes on a context row}
		\If $\txInit_{i} = 1$ \Then
		\[
			\begin{cases}
				\If \peekContext _{i} = 0 ~ \Then \txInit _{i + 1} = 1 \\
				\If \peekContext _{i} = 1 ~ \Then \txExec _{i + 1} = 1 \\
			\end{cases}
		\]
	\item \If $\txExec_{i} = 1$ \Then $\txExec_{i + 1} + \txFinl_{i + 1} = 1$
	\item
		\label{hub: heartbeat: finalization phase finishes on a transaction row}
		\If $\txFinl_{i} = 1$ \Then $\txFinl_{i + 1} = 1 - \peekTransaction_{i}$
\end{enumerate}
\saNote{}
Just as above we note that the case $\txFinl_{i} = 1$ \et $\peekTransaction_{i} = 1$ was already known.
Indeed, in that case the absolute transaction number must change at the next row due to constraint~(\ref{hub: heartbeat: abs tx num increments}).
It follows from constraint,
see section~(\ref{hub: heartbeat: acceptable tx phases at first row of new transaction}),
that $\locAcceptableTransactionPhaseFlagsAtFirstRowOfNewTransaction$.
By flag exclusivity,
see section~(\ref{hub: heartbeat: tx phase flag exclusivity}),
it follows in particular that $\txFinl_{i + 1} = 0$.

The above enforces the basic cycling behaviour as depicted in figure~\ref{fig: processing phase transition graph}. Prewarming rows (if any) lead to initialization rows which lead to execution rows which lead to finalization rows. Furthermore, the finalization phase may only end on a row that peeks into transaction data. The number of rows of each phase will be specified later.
